An Improved Metric for the Analysis of Swarms

### 2018-02-27 paper.tex
Future Work Update

A possible adaptation to both of these areas of research would be to use the swarm perimeter detection to identify a subset of agents then reducing the field effect of those agents to increase the agent density at the perimeter. Increasing the density would allow increased coverage of any sensor arrays that the swarm was using at the swarm edge. The issue with introducing heterogeneous field effects is that existing coordination techniques are required. The cohesion/repulsion metric discussed in this paper would still work within this environment as a tool to identify swarm stability. this is due to the metric being based upon inter-agent effects rather than physical distribution.

>>>>

A possible adaptation to both of these areas of research would be to use the swarm perimeter detection to identify a subset of agents then reducing the field effect of those agents to increase the agent density at the perimeter. Increasing the density would allow increased coverage of any sensor arrays that the swarm was using at the swarm edge. The issue with introducing heterogeneous field effects is that existing distance based metric would not allow the swarm's structure to be analysed correctly. The cohesion/repulsion metric discussed in this paper would still work within this environment as a tool to identify swarm stability. This is due to the metric being based upon inter-agent effects rather than physical distribution.
